### 2013-02-14 patchy-selection-paper.tex
WorkingWiki importation

\plr{Aim here is to discuss transition to discrete model?}

We can extend this reasoning to multiple patches ($>2$) within our population's range
where our $B$ allele can facilitate local adaptation. Under our
assumptions of mutational exclusion and rapid establishment, each one
of these patches will adapt through a single copy of the $B$
alllele. The occupation of our different patches by the $B$ allele will form a
discrete state markov chain, where the states of the chain are which patches have
been colonized so far by $B$, and which colonized patches have shared
versus distinct copy of $B$.

For simplicity we will assume that each of these patches has
the same size and geometry (i.e.\ same $E$). A particular patch adapts in parallel through an independent
instance of the $B$ mutation at rate $2 s_B \mu \rho A$.
While, if patches $1$ through $k$ are already occupied by
established copies of the $B$ allele, and these patches are at
distances $R_1,~\cdots,~R_k$ away from our patch, the rate of
adaptation through migration in our patch is 
\begin{equation}
\sum_{i=1}^{k} 2 s_B \rho E \exp(- \sqrt{s_m} R_k/\sigma).
\end{equation}
Once again the compound parameter $2s_B \rho$ will function to
scale the times between events (parallel adaptation or the spread of a
migrant), and so is critical to the time-scale over which
adaptation occurs. However, this compound parameter again has no effect on
the final configuration of the pattern of which patches have adapted
in parallel versus have shared genetic basis to their adaptive
response to the poor environment.

The states of this

%Furthermore, in the model of discrete demes connected by symmetric weak migration, 
%the final distribution of types depends only on the ratio of mutation to migration rates,
%and that the number of independently arisen types follows the Ewens distribution, with parameter $\mu/m$.
%In Figure \ref{fig:discbyratio} we plot mean number of types and size (number of demes occupied) of a sampled type,
%for a model with 20 interconnected demes, across different parameter values.  
%This indicates that we need the population-scaled mutation and migration rates 
%to be within a factor of about 100 of each other for parallel adaptation to leave an interesting pattern.  
%If migration is faster, then a single type is likely to take over, while if migration is weaker, each deme is likely to come up with its own type.

%\begin{figure}[ht]
% \begin{center}
 %  \includegraphics{discrete-by-ratio}
 %\caption{ %
 %The mean number of types and the mean number of demes occupied by a sampled type, in a discrete model with 20 demes,
 %plotted as a function of the ratio of migration to mutation probabilities.
% Note the log scale on the horizontal axis.
% \label{fig:discbyratio}
 %}
 %\end{center}
%\end{figure}

Also note that the properties of the discrete model are independent of the {\em sizes} of the demes themselves--- we have assumed away all such dependence.
This is complementary to the results of \cite{softsweepsII}, who showed that multiple mutations are likely to arise {\em within} a panmictic deme
if the population-scaled mutation rate $2 N \mu$ is greater than $1$.

%%%%%%%%%
\section{Length of the hitchhiking haplotype}
\label{ss:haplotype_length}

@@

%%%
\subsection{Limiting distributions}

>>>>

We can extend this reasoning to multiple patches of unadapted habitat 
in which the $B$ allele can facilitate local adaptation. 
Under our assumptions of mutational exclusion and rapid establishment, 
each patch will adapt through establishment of a single copy of the $B$ allele, 
either by migration or mutation.
Since we assume that the times between successive establishments is the result of many nearly-independent attempts
with small probability of success,
the process of occupation is well approximated by a discrete-state Markov chain,
whose state is the labeling of patches according to the colonizing allele
(or none, for those that haven't yet adapted).

If not yet adapted,
a patch of area $A$ will acquire the adaptation by new mutation at rate $2 s_B \mu \rho A/\xi^2$.
Without loss of generality, assume that patches $1, \ldots, k$ are already adapted,
and these patches are at distances $R_1, \ldots, R_k$ away from this unadapted patch, 
then the total rate of adaptation through migration is
\begin{equation}
  \frac{ s_B (s_B+s_m) \rho A}{\xi^2} \sum_{i=1}^{k} \exp\left(- \sqrt{s_m} R_i/\sigma\right),
\end{equation}
and the probability that the adaptation is from patch $i$ is $\exp\left(- \sqrt{s_m} R_i/\sigma\right)/\sum_{j=1}^{k} \exp\left(- \sqrt{s_m} R_j/\sigma\right)$.
These specify the transition rates of the process.

Since the compound parameter $s_B \rho / \xi^2$ is common to both rates,
it functions only as a time scaling of the process, 
and therefore has no effect on the final configuration of the pattern of which patches have adapted
in parallel versus have shared genetic basis to their adaptive response to the poor environment.

Also note that we can rescale time by the typical patch size, and introduce a parameter, say $a_k = A_k/\bar A$,
making the properties (other that the time scaling) of the discrete model independent of the \emph{numerical sizes} of the demes themselves.
This is complementary to the results of \cite{softsweepsII}, who showed that multiple mutations are likely to arise \emph{within} a panmictic deme
if the population-scaled mutation rate $2 N \mu$ is greater than $1$.

\plr{conclusion?}

%%%%%%%%%
\subsection{Length of the hitchhiking haplotype}
\label{ss:haplotype_length}

@@

%%%
\subsubsection{Limiting distributions}
